The Astropy Project

### 2017-11-13 main.tex
Add ECSV APE reference

The \package{astropy.io} subpackage provides support for reading and writing
data to a variety of ASCII and binary file formats, such as a wide range of
ASCII data table formats, FITS, and VOTable.
It also provides a unified interface for reading and writing data with these
different formats using the \package{astropy.table} subpackage.
For many common cases this simplifies the process of file input/output and
reduces the need to master the separate details of all the I/O packages within
\astropypkg.
% This functionality is still in active development and the number of supported
% formats will be increasing.

@@

        One of the problems when storing a table in an ASCII format is
        preserving table meta-data such as comments, keywords and column data
        types, units, and descriptions. Using the newly defined \emph{Enhanced
        Character Separated Values} (ECSV) format it is now possible to write
        a table to an ASCII-format file and read it back with no loss of
        information. The ECSV format has been designed to be both
        human-readable and compatible with most simple CSV readers.

>>>>

The \package{astropy.io} subpackage provides support for reading and writing
data to a variety of ASCII and binary file formats, such as a wide range of
ASCII data table formats, FITS, and VOTable.
It also provides a unified interface for reading and writing data with these
different formats using the \package{astropy.table} subpackage.
For many common cases this simplifies the process of file input and output and
reduces the need to master the separate details of all the I/O packages within
\astropypkg.

@@

        One of the problems when storing a table in an ASCII format is
        preserving table meta-data such as comments, keywords and column data
        types, units, and descriptions. Using the newly defined \emph{Enhanced
        Character Separated Values} (ECSV,  \citet{ape6}) format it is now
        possible to write a table to an ASCII-format file and read it back
        with no loss of information. The ECSV format has been designed to be
        both human-readable and compatible with most simple CSV readers.
